Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-04-02 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Cleanup HF data, add script, figures, remove old figures, update latex

\begin{figure}[h!]
  \centering
  \includegraphics[width=4.5in]{../Figures/ST_NG_HRR}\\
  \includegraphics[width=4.5in]{../Figures/ST_Gas_HRR}\\
  \caption[Heat release rates for the natural gas and gasoline foam fires]{Heat release rates for the natural gas and gasoline fires.}
  \label{HRR}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=4.5in]{../Figures/ST_PUF_HRR}\\
  \caption[Heat release rates for the polyurethane foam fires]{Heat release rates for the polyurethane foam fires.}
  \label{HRR2}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \includegraphics[width=4.5in]{../Figures/Fig9}\\
  \includegraphics[width=4.5in]{../Figures/Fig10}\\
  \includegraphics[width=4.5in]{../Figures/Fig11}\\
  \caption[Total heat flux versus time for natural gas, gasoline, and foam fires]{Total heat flux versus time for natural gas, gasoline, and foam fires.}
  \label{Flux}
\end{figure}

@@

Examples of a set of TIFF images for each fuel are shown in Figures~\ref{flame_height_comp_FHNG80_1} through \ref{flame_height_comp_FHPUF_1}.   Each figure has 56 sequential images from the video segment.  The images total almost 2~s of actual burn time.  Notice how the flame height cycles up and down in each of the sequences.  These images provide additional information and continuity of the motion of the flame so that the analysis is less likely to miss and extreme (minimum or maximum) position when compared to the still photographs.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/flame_height_comp_FHNG80}\\
	\caption[Example of sequential video frames sampled from a natural gas fueled experiment]{Example of sequential video frames sampled from a natural gas fueled experiment.  In this set of images, which spans almost two seconds, the visual continuous flame height fluctuates from approximately 0.6~m to 1.1~m.}
	\label{flame_height_comp_FHNG80_1}
\end{figure}

@@

Temperatures were also measured on the backside of the wall, along the vertical centerline of the burners, Figure~\{NCTW_Back_Cent_comp}. The temperature difference between the peak average temperatures on the front (fire side) of the wall at 0.2~m above the burner vs the corresponding temperatures on the backside of the wall have a difference of at least 400~$^\circ$C.  It is consistent with the temperature data shown in Figures~\ref{NCTW_Surf_Center_comp} and \ref{NCTW_Surf_Edge_comp}, that as the burners were moved away from the wall the temperature differences are reduced.

\begin{figure}[p]
	\centering
	\includegraphics[width=3.5in]{../Figures/NCTW_NG_TC_Surface_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_TC_Surface_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Surface_Center_Avg}\\

	\caption[Composite graph of the wall temperatures along the centerline of the burners]{Composite graph of the wall temperatures along the centerline of the burners for each fuel. The peak temperatures are averages of replicate experiments for each instrument location at each position from the wall. Beginning with the top graph position and moving down the graph for natural gas, gasoline, and polyurethane foam are presented.}
	\label{NCTW_Surf_Center_comp}
\end{figure}

@@

Figures~\ref{NCTW_HF_Center_Comp} and {NCTW_HF_Edge_Comp} show the results from the arrays of total heat flux gauges located along the vertical centerline and the edge of the burners for each fuel.  The sensing surface of the gauges were installed flush with the wall surface and exposed to the fire. In each graph, the averaged peak heat flux for each of the replicate experiments and each position is shown.  Moving from 0.2~m above the top surface of the burner up to 1.2~m above the top of the burner surface in increments of 0.2~m.  Reviewing the graph for each fuel demonstrates how the heat flux at the wall decreased as the position of the burner was moved away from the wall.  (Review video and tie in ST TC graph with edge peak NG at 0.15)

@@

\chapter{Instrumented Gypsum Board Wall Experiments}
Purpose
\section{Experimental Arrangement}
This series of experiments combined the instrumentation used in the non-combustible wall experiments with gypsum wallboard, which has a combustible paper surface.  A free standing, steel frame with a panel of gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.  The fires were initially placed at predetermined, fixed positions away from the wall. The burner was moved toward the wall until the burner was against the wall.  If the results indicated that no burn pattern would result from a given combination of fuel and position, then that fuel and position combination were eliminated from the remainder of the test matrix.

The thermocouple arrangement for these experiments, only had one vertical array of thermocouples.  The thermocouples were positioned between the two vertical arrays of heat flux gauges as shown in Figure~ref\{Instrumented_GB_Wall}  As a means of ensuring contact between the gypsum wallboard and the thermocouple, the thermocouples were installed by pulling the positive and negative wires through holes drilled on the horizontal centerline between the heat flux gauges and positioning the bead of the thermocouple in a slit in the paper face made with a razor blade.  A thermocouple installed in this manner shown in Figure~ref\

@@

>>>>

\begin{figure}[!ht]
  \centering
  \includegraphics[width=4.5in]{../Figures/ST_NG_HRR}\\
  \includegraphics[width=4.5in]{../Figures/ST_Gas_HRR}\\
  \caption[Heat release rates for the natural gas and gasoline foam fires]{Heat release rates for the natural gas and gasoline fires.}
  \label{HRR}
\end{figure}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=4.5in]{../Figures/ST_PUF_HRR}\\
  \caption[Heat release rates for the polyurethane foam fires]{Heat release rates for the polyurethane foam fires.}
  \label{HRR2}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \includegraphics[width=3.5in]{../Figures/HF_NG}\\
  \includegraphics[width=3.5in]{../Figures/HF_GAS}\\
  \includegraphics[width=3.5in]{../Figures/HF_PUF}\\
  \caption[Total heat flux versus time for natural gas, gasoline, and foam fires]{Total heat flux versus time for natural gas, gasoline, and foam fires.}
  \label{Flux}
\end{figure}

@@

Examples of a set of TIFF images for each fuel are shown in Figures~\ref{flame_height_comp_FHNG80_1} through \ref{flame_height_comp_FHPUF_1}.   Each figure has 56 sequential images from the video segment.  The images total almost 2~s of actual burn time.  Notice how the flame height cycles up and down in each of the sequences.  These images provide additional information and continuity of the motion of the flame so that the analysis is less likely to miss and extreme (minimum or maximum) position when compared to the still photographs.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/flame_height_comp_FHNG80}\\
	\caption[Example of sequential video frames sampled from a natural gas fueled experiment]{Example of sequential video frames sampled from a natural gas fueled experiment.  In this set of images, which spans almost two seconds, the visual continuous flame height fluctuates from approximately 0.6~m to 1.1~m.}
	\label{flame_height_comp_FHNG80_1}
\end{figure}

@@

Temperatures were also measured on the backside of the wall, along the vertical centerline of the burners, Figure~\ref{NCTW_Back_Cent_comp}. The temperature difference between the peak average temperatures on the front (fire side) of the wall at 0.2~m above the burner vs the corresponding temperatures on the backside of the wall have a difference of at least 400~$^\circ$C.  It is consistent with the temperature data shown in Figures~\ref{NCTW_Surf_Center_comp} and \ref{NCTW_Surf_Edge_comp}, that as the burners were moved away from the wall the temperature differences are reduced.

\begin{figure}[p]
	\centering
	\includegraphics[width=3.5in]{../Figures/NCTW_NG_TC_Surface_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_TC_Surface_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Surface_Center_Avg}\\
	\caption[Composite graph of the wall temperatures along the centerline of the burners]{Composite graph of the wall temperatures along the centerline of the burners for each fuel. The peak temperatures are averages of replicate experiments for each instrument location at each position from the wall. Beginning with the top graph position and moving down the graph for natural gas, gasoline, and polyurethane foam are presented.}
	\label{NCTW_Surf_Center_comp}
\end{figure}

@@

Figures~\ref{NCTW_HF_Center_Comp} and \ref{NCTW_HF_Edge_Comp} show the results from the arrays of total heat flux gauges located along the vertical centerline and the edge of the burners for each fuel.  The sensing surface of the gauges were installed flush with the wall surface and exposed to the fire. In each graph, the averaged peak heat flux for each of the replicate experiments and each position is shown.  Moving from 0.2~m above the top surface of the burner up to 1.2~m above the top of the burner surface in increments of 0.2~m.  Reviewing the graph for each fuel demonstrates how the heat flux at the wall decreased as the position of the burner was moved away from the wall.  (Review video and tie in ST TC graph with edge peak NG at 0.15)

@@

\chapter{Instrumented Gypsum Board Wall Experiments}

\section{Experimental Arrangement}
This series of experiments combined the instrumentation used in the non-combustible wall experiments with gypsum wallboard, which has a combustible paper surface.  A free standing, steel frame with a panel of gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.  The fires were initially placed at predetermined, fixed positions away from the wall. The burner was moved toward the wall until the burner was against the wall.  If the results indicated that no burn pattern would result from a given combination of fuel and position, then that fuel and position combination were eliminated from the remainder of the test matrix.

The thermocouple arrangement for these experiments, only had one vertical array of thermocouples.  The thermocouples were positioned between the two vertical arrays of heat flux gauges as shown in Figure~\ref{Instrumented_GB_Wall}  As a means of ensuring contact between the gypsum wallboard and the thermocouple, the thermocouples were installed by pulling the positive and negative wires through holes drilled on the horizontal centerline between the heat flux gauges and positioning the bead of the thermocouple in a slit in the paper face made with a razor blade.  A thermocouple installed in this manner shown in Figure {\bf fig reference}

@@

% \begin{figure}
% 	\centering
% 	\includegraphics[width=\textwidth]{../Figures/Instrumented_GB_Wall}\\
% 	\caption[Diagram of the instrumented non-combustible wall]{Diagram of the instrumented non-combustible wall. Two vertical arrays of total heat flux gauges and thermocouples were installed along the centerline of the burner and along the right edge of the burner.}
% 	\label{Instrumented_GB_Wall}
% \end{figure}
